---
title: "GoogleSheets_EmailTidyUp"
author: "Office of Marketing and Brand Management"
date: "4/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(knitr)
```

```{r eval=FALSE, include=FALSE}
path <- "C:/Users/christine.iyer/Box/FY20_EmailAnalytics/FY20_Email_HS_AppGen/EmailTargetX.xlsx"
August2017 <- read_excel(path, sheet = "August2017")
names(August2017)
August2017 <- August2017 %>% mutate(Delivered = 0) %>% select(`Broadcast: Broadcast Name`, Date, Sent, Delivered, everything())
colnames(August2017) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")

# August2017 <- August2017 %>% mutate(
#   FY = 
#   
#   Campaign = stringr::str_extract(`Broadcast: Broadcast Name`, "^.{18}")) %>% select(Campaign, everything())

```



# a <- "Goldman Sachs; Morgan Stanley"
# b <- "UBS; Wells Fargo; Wachovia"
# c <- "Bank of America"
# d <- rbind.data.frame(a,b,c) 
# d$Bank <- d$c..Goldman.Sachs..Morgan.Stanley....UBS..Wells.Fargo..Wachovia...
# 
# 
# tbl2 <- d %>% separate(Bank, 
#         sep = "; ", into = c("a", "b", "c"))
# kable(tbl2)


#path <- "C:/Users/christine.iyer/Box/FY20_EmailAnalytics/FY20_Email_HS_AppGen/EmailTargetX.xlsx"
September2017 <- read_excel(path, sheet = "September2017")


colnames(September2017) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")




October2017 <- read_excel(path, sheet = "October2017")
colnames(October2017) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")
October2017


November2017 <- read_excel(path, sheet = "November2017")
colnames(November2017) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")


December2017 <- read_excel(path, sheet = "December2017")
colnames(December2017) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")

January2018 <- read_excel(path, sheet = "January2018")
colnames(January2018) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")


February2018 <- read_excel(path, sheet = "February2018")
colnames(February2018) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")



March2018 <- read_excel(path, sheet = "March2018")
colnames(March2018) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")



April2018 <- read_excel(path, sheet = "April2018")
colnames(April2018) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")



May2018 <- read_excel(path, sheet = "May2018")
May2018 <- May2018 %>% select(`Broadcast: Broadcast Name`, Date:`Unsub. Rate`)
colnames(May2018) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")


June2018 <- read_excel(path, sheet = "June2018")
June2018 <- June2018 %>% select(`Broadcast: Broadcast Name`, Date:`Unsub. Rate`)
colnames(June2018) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")
names(June2018)
names(February2018)


FY2019 <- read_excel(path, sheet = "FY2019")
FY2019 <- FY2019 %>% select(`Broadcast: Broadcast Name`, `Day of Start.Date`, Sent ,Delivered, Opens, Clicks, `Opt Outs`, Bounces, `Bounce Rate`, CTOR, CTR, `Open Rate`, `Unsubscribe Rate`)
colnames(FY2019) <- c("Broadcast", "Date", "Sent", "Delivered","Opens", "Clicks", "OptOuts","Bounces","BounceRate","CTOR","CTR","OpenRate","UnsubRate")
names(FY2019)
names(February2018)



AllEMails <- rbind.data.frame(August2017, September2017, October2017, December2017, January2018, February2018, March2018, April2018, May2018, June2018, FY2019)
kable(head(AllEMails))

write.csv(AllEMails, "C:/Users/christine.iyer/Box/FY20_EmailAnalytics/FY20_Email_HS_AppGen/AllEmailsTidied.csv", row.names = F )
```

```{r}
allEmails1 <- read.csv("C:/Users/christine.iyer/Box/FY20_EmailAnalytics/FY20_Email_HS_AppGen/AllEmails1.csv", header = T, stringsAsFactors = F)

kable(allEmails1 %>% 
  filter(Link == "Unsubscribe") %>% 
  group_by(Name, Date.Time.Sent) %>% 
  summarise(Unsubs = sum(Unique_Clicks),
            Sent = sum(Emails.Sent) ,
            DR =  sum(Deliverability.Rate) *100,
            Delivered = round(Sent * DR,0), 
            UnsubRate = Unsubs/Delivered*100, 
            CTR = mean(Net_CTR) *100, 
            OpenRate = sum(Open.Rate)*100))
```

